sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-03-10 doc/paper-jss/pcod.Rmd
Remove aes_string #13

```{r plot-map}
plot_map <- function(dat, column) {
  ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    facet_wrap(~year) +
    coord_fixed()
}
```

@@

```{r plot-all-effects, fig.cap="Model predictions based on all fixed effects and random effects.", fig.pos='ht', fig.align='center'}
plot_map(pred_qcs, "exp(est)") +
  scale_fill_viridis_c(trans = "log10") 
```

@@

```{r plot-fix-defects, fig.cap="Predictions based on only the non-random field elements.", fig.pos='ht', fig.align='center'}
plot_map(pred_qcs, "exp(est_non_rf)") +
  scale_fill_viridis_c(trans = "sqrt")
```

@@

```{r plot-spatial-effects, fig.cap="Spatial random effects only.", fig.pos='ht', fig.align='center'}
plot_map(pred_qcs, "omega_s") +
  scale_fill_gradient2()
```

@@

```{r plot-spatiotemporal-effects, fig.cap="Spatiotemporal random effects only.", fig.pos='ht', fig.align='center'}
plot_map(pred_qcs, "epsilon_st") +
  scale_fill_gradient2()
```

>>>>

```{r plot-map}
plot_map <- function(dat, column) {
  ggplot(dat, aes(X, Y, fill = {{ column }})) +
    geom_raster() +
    facet_wrap(~year) +
    coord_fixed()
}
```

@@

```{r plot-all-effects, fig.cap="Model predictions based on all fixed effects and random effects.", fig.pos='ht', fig.align='center'}
plot_map(pred_qcs, exp(est)) +
  scale_fill_viridis_c(trans = "log10") 
```

@@

```{r plot-fix-defects, fig.cap="Predictions based on only the non-random field elements.", fig.pos='ht', fig.align='center'}
plot_map(pred_qcs, exp(est_non_rf)) +
  scale_fill_viridis_c(trans = "sqrt")
```

@@

```{r plot-spatial-effects, fig.cap="Spatial random effects only.", fig.pos='ht', fig.align='center'}
plot_map(pred_qcs, omega_s) +
  scale_fill_gradient2()
```

@@

```{r plot-spatiotemporal-effects, fig.cap="Spatiotemporal random effects only.", fig.pos='ht', fig.align='center'}
plot_map(pred_qcs, epsilon_st) +
  scale_fill_gradient2()
```
